% SYNTHETIC CV SOURCE — public test fixture only.
%
% This is a fully synthetic CV for the fictional candidate "Jordan Avery". It
% exists so the material-generation test suite has a structure-preserving CV
% template to tailor in the public mirror. It contains no real personal data.
% In the private canonical repo this path holds the operator's real CV source,
% which is never published.

\documentclass[11pt]{extarticle}
\usepackage[a4paper,margin=18mm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\pagestyle{empty}

\titleformat{\section}{\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\begin{document}

\begin{center}
  {\LARGE \textbf{JORDAN AVERY, PhD}} \\
  \small
  Email: jordan.avery@example.com \quad
  LinkedIn: linkedin.com/in/jordan-avery-example
\end{center}

\section*{Professional Summary}
Senior AI and data science leader who builds and scales teams, ships production
machine learning, and aligns delivery to strategy. Comfortable owning end to end
platform decisions and turning research into reliable products.

\section*{Core Capabilities}
\textbf{AI Strategy:} enterprise roadmaps and grounded delivery\\[2pt]
\textbf{ML Engineering:} production models, MLOps, and platforms\\[2pt]
\textbf{Leadership:} building, scaling, and mentoring teams

\section*{Professional Experience}
\textbf{Head of Data Science, Northwind Robotics} \hfill 2022--2026\\
\begin{itemize}
\item Led applied AI strategy and delivery across multiple product teams.
\item Built and scaled a data science function and its hiring framework.
\end{itemize}
\textbf{Lead AI Engineer, Acme FinTech} \hfill 2018--2022\\
\begin{itemize}
\item Shipped production machine learning models and MLOps pipelines.
\item Partnered with leadership on AI roadmaps and platform decisions.
\end{itemize}

\section*{Education}
PhD, Synthetic University. Research in applied machine learning.

\end{document}
